Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-29 article.tex
add missing values for full method in Appendix

\begin{table}[h]
\caption{Performance (top: AUROC, bottom: AUPRC) on specific datasets with different methods.}
\label{tab:results_appendix}
\centering
\small
\begin{tabular}{| l | c c c c c c |}
\hline
& \multicolumn{6}{c|}{AUROC}\\
\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise} \\
\hline
\hline
Averaging     & 0.947 & 0.943 & 0.920 & 0.942 & 0.959 & 0.934 \\
Full method   &  &  &  & & &\\
PC & 0.782 & 0.920 &  0.846 & 0.897  & 0.898  & 0.873 \\
GTE & 0.846 & 0.905 & 0.848 & 0.899 & 0.905 & 0.879\\
GENIE3 & 0.781 &  0.924 & 0.879 & 0.902 & 0.886 &  0.890 \\ \hline \hline
& \multicolumn{6}{c|}{AUPRC}\\ \hline
Averaging     & 0.320 & 0.429 & 0.262 & 0.478 & 0.443 & 0.412 \\
Full method   &  &  &  & & &\\
PC & 0.074 & 0.218 & 0.082 & 0.165  & 0.193 & 0.135 \\
GTE & 0.094 & 0.211 & 0.081 & 0.165 & 0.210 & 0.144\\
GENIE3 & 0.128 & 0.273 & 0.116 & 0.309 & 0.256 & 0.224\\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[h]
\caption{Performance (top: AUROC, bottom: AUPRC) on specific datasets with different methods.}
\label{tab:results_appendix}
\centering
\small
\begin{tabular}{| l | c c c c c c |}
\hline
& \multicolumn{6}{c|}{AUROC}\\
\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise} \\
\hline
\hline
Averaging     & 0.947 & 0.943 & 0.920 & 0.942 & 0.959 & 0.934 \\
Full method   & 0.955 & 0.944 &  0.925 & 0.946 & 0.961 & 0.941 \\
PC & 0.782 & 0.920 &  0.846 & 0.897  & 0.898  & 0.873 \\
GTE & 0.846 & 0.905 & 0.848 & 0.899 & 0.905 & 0.879\\
GENIE3 & 0.781 &  0.924 & 0.879 & 0.902 & 0.886 &  0.890 \\ \hline \hline
& \multicolumn{6}{c|}{AUPRC}\\ \hline
Averaging     & 0.320 & 0.429 & 0.262 & 0.478 & 0.443 & 0.412 \\
Full method   & 0.334 & 0.413 &  0.260 & 0.486 & 0.452 & 0.432\\
PC & 0.074 & 0.218 & 0.082 & 0.165  & 0.193 & 0.135 \\
GTE & 0.094 & 0.211 & 0.081 & 0.165 & 0.210 & 0.144\\
GENIE3 & 0.128 & 0.273 & 0.116 & 0.309 & 0.256 & 0.224\\ \hline
\end{tabular}
\end{table}
